---
title: "AUCplots"
author: "TriDoan"
date: "Saturday, September 12, 2015"
output: pdf_document
---

This is R script to plot multiple AUCs in predict movie sentiment.

```{r}
library(dplyr)
setwd("c:/AAAI/AUC")
df <- read.csv("Bagging.csv",stringsAsFactors=FALSE)

```

Extract needed field

```{r, echo=FALSE}
actual  <- data.frame(t(sapply(df[,2], function(y) strsplit(y,split=":")[[1]])))
predicted <- data.frame(t(sapply(df[,3], function(y) strsplit(y,split=":")[[1]])))

bagging.labels  <- as.data.frame(cbind(df$inst,actual[,2],df[,ncol(df)]))
row.names(bagging.labels) <- seq_len(nrow(bagging.labels))
colnames(bagging.labels) <- c("inst","label","predict")


#class.predicted  <- as.data.frame(cbind(df$inst,predict[,2],df[,ncol(df)]))
#row.names(bagging.predicted) <- seq_len(nrow(bagging.predicted))

rm(actual)
rm(predicted)

write.table(bagging.labels,file="baggingPrediction.csv",sep=",",row.names=FALSE,col.names=TRUE)    
```

Similarly, for Naive Bayes
``{r}
df <- read.csv("naiveBayes.csv",stringsAsFactors=FALSE)
actual  <- data.frame(t(sapply(df[,2], function(y) strsplit(y,split=":")[[1]])))

NaiveBayes.labels  <- as.data.frame(cbind(df$inst,actual[,2],df[,ncol(df)]))
row.names(NaiveBayes.labels) <- seq_len(nrow(NaiveBayes.labels))
colnames(NaiveBayes.labels) <- c("inst","label","predict")
write.table(NaiveBayes.labels,file="naivebayes.csv",sep=",",row.names=FALSE,col.names=TRUE)    


rm(actual)

```

Similarly, for Logistic
``{r}
df <- read.csv("logistic.csv",stringsAsFactors=FALSE)
actual  <- data.frame(t(sapply(df[,2], function(y) strsplit(y,split=":")[[1]])))

Logistic.labels  <- as.data.frame(cbind(df$inst,actual[,2],df[,ncol(df)]))
row.names(Logistic.labels) <- seq_len(nrow(Logistic.labels))
colnames(Logistic.labels) <- c("inst","label","predict")
write.table(Logistic.labels,file="logisticPrediction.csv",sep=",",row.names=FALSE,col.names=TRUE)    

rm(actual)
```

Similarly, for Random Forest
``{r}
df <- read.csv("randomForest.csv",stringsAsFactors=FALSE)
actual  <- data.frame(t(sapply(df[,2], function(y) strsplit(y,split=":")[[1]])))

randomForest.labels  <- as.data.frame(cbind(df$inst,actual[,2],df[,ncol(df)]))
row.names(randomForest.labels) <- seq_len(nrow(randomForest.labels))
colnames(randomForest.labels) <- c("inst","label","predict")
write.table(randomForest.labels,file="randomForestPrediction.csv",sep=",",row.names=FALSE,col.names=TRUE)    

rm(actual)

```

Similarly, for SVM
``{r}
df <- read.csv("SVM.csv",stringsAsFactors=FALSE)
actual  <- data.frame(t(sapply(df[,2], function(y) strsplit(y,split=":")[[1]])))

svm.labels  <- as.data.frame(cbind(df$inst,actual[,2],df[,ncol(df)]))
row.names(svm.labels) <- seq_len(nrow(svm.labels))
colnames(svm.labels) <- c("inst","label","predict")
write.table(svm.labels,file="svmPrediction.csv",sep=",",row.names=FALSE,col.names=TRUE)    

rm(actual)
```
plot multiple AUC of multiple classifiers 
```{r}
library(ROCR)
data(ROCR.simple)
pred <- prediction( ROCR.simple$predictions, ROCR.simple$labels )
pred2 <- prediction(abs(ROCR.simple$predictions + 
                        rnorm(length(ROCR.simple$predictions), 0, 0.1)), 
        ROCR.simple$labels)
perf <- performance( pred, "tpr", "fpr" )
perf2 <- performance(pred2, "tpr", "fpr")
plot( perf, colorize = TRUE)
plot(perf2, add = TRUE, colorize = TRUE)

