---
title: "LearningAlgorithm For data mining Task"
author: "TriDoan"
date: "Sunday, August 23, 2015"
output: html_document
---

Prepare to load corpus data 

```{r}
setwd("C:/aclImdb")
library(tm)

nb_pos <- Corpus(DirSource("./train/pos"), readerControl = list(language = "en"))
nb_neg <- Corpus(DirSource("./train/neg"),readerControl = list(language = "en"))
nb_all <- c(nb_pos, nb_neg, recursive = T)

meta(nb_all[[1]])
ids <- sapply( 1 : length(nb_all), function(x) meta(nb_all[[x]], "id"))

head(ids)
scores <- as.numeric(sapply(ids, function(x) sub("[0-9]+_([0-9]+)\\.txt", "\\1", x)))
scores <- factor(ifelse(scores >= 5, "positive", "negative"))

nb_all <- tm_map(nb_all, content_transformer(removeNumbers))
nb_all <- tm_map(nb_all, content_transformer(removePunctuation))
nb_all <- tm_map(nb_all, content_transformer(tolower))
nb_all <- tm_map(nb_all, content_transformer(removeWords), stopwords("english"))
nb_all <- tm_map(nb_all, content_transformer(stripWhitespace))

nb_dtm <- DocumentTermMatrix(nb_all)
nb_dtm <- removeSparseTerms(x = nb_dtm, sparse = 0.98)

dim(nb_dtm)
inspect(nb_dtm[10:16, 1:6])


nb_dtm <- weightBin(nb_dtm)




```
Convert into data frame

```{r}
 nb_df <- as.data.frame(as.matrix(nb_dtm))
```
Load library
```{r}
library(caret)
library(e1071)
set.seed(12345)

```
Create train and test set

```{r}
nb_sampling_vector <- createDataPartition(scores, p = 0.80, list = FALSE)
nb_df_train <- nb_df[nb_sampling_vector,]
nb_df_test <- nb_df[-nb_sampling_vector,]


scores_train = scores[nb_sampling_vector]
scores_test = scores[-nb_sampling_vector]

df_train <-  as.data.frame(nb_df_train)

df_train$class <- scores_train

```

Without further preprocessing data, using Naive Bayes we can achieve

accuracy =  0.8158

```{r}

nb_model <- naiveBayes(nb_df_train, scores_train)
nb_train_predictions <- predict(nb_model, nb_df_train)

nb_test_predictions <- predict(nb_model, nb_df_test)
mean(nb_test_predictions == scores_test)

```
Now we check other model

1. Random Forest
accuracy = 0.834

```{r}
library("randomForest")

rf<- randomForest(nb_df_train, scores_train)

rf_test_prediction <- predict(rf, nb_df_test, type="class")
mean(rf_test_prediction == scores_test)
```

2. SVM

accuracy = 0.8578
```{r}

library(e1071)
SVM_model <- svm(nb_df_train, scores_train,type='C',kernel='radial',probability = FALSE)

SVM_test_prediction <- predict(SVM_model, nb_df_test,type="class")
mean(SVM_test_prediction == scores_test)

```
3. Multivariate Adaptive Regression Splines

accuracy = 0.8188

```{r}
library(earth)

mars_model <-  earth(nb_df_train, scores_train)
mars_test_prediction <- predict(mars_model, nb_df_test,type="class")
mean(mars_test_prediction == scores_test)


```
 gbm

```{r}
library(gbm)
gbm_model = gbm(class~., data= df_train,distribution="bernoulli",interaction.depth=3,shrinkage=0.005 ,cv.folds=10)

best.iter <- gbm.perf(GBM_model,method="cv")

train_pred <- predict.gbm(GBM_model,trainset,best.iter)
test_pred <- predict.gbm(GBM_model,testset,best.iter)
